\huge \systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-10 poster.tex
final logo figured
moved around sections and poster

\begin{block}{Turtle/LOGO Graphics}

  \newcommand{\dreamSize}{5.5cm}
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{9 (of 132) Tasks}}\\\hline
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_3_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow1_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow2_random_1.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/hexa_vh.png}&
        \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_5_h.png}\\
%    \includegraphics[width = \dreamSize]{turtleTasks/circle/trimmed/train_circle_10_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/smooth_spiral4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/los/trimmed/train_los_3_1_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/iter2_h.png}\\\hline
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1748505267_norm.png}&
  \end{tabular}\hspace{4cm}%
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{9 samples from learned DSL}}\\\hline
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/4361002260.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/5809723215.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/5818934795_norm.png}\\
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/6027771181.png}\\
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1950268419.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/6770710484.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/7045328293.png}\\
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/7623700519.png}&
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/8879622788.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/9150025422.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/9666602433.png}\\\hline
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1748505267_norm.png}&
    \end{tabular}
  Learn probabilistic program (a regex) $p_n$ from $K$ strings $x_n = \left\{y_n^k \right\}_{k = 1}^K$.

  Likelihood model:
  $$\probability [x_n|p_n] = \prod_{k = 1}^K \probability[y_n^k|p_n]$$
\begin{figure}
\centering
%\tiny
\tabcolsep=2pt
\vspace{0pt}
\begin{tabular}{cc}
\begin{tabular}{ccc}
\multicolumn{3}{c}{Tasks:}\\
\hline
cut&F &Moss Side \\ 
control&CL &Burnage \\
control&F & City Centre\\
cut& PCFL& Brooklands \\
\multicolumn{3}{c}{Learned generative models:}\\
\hline
\scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash
u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash
u\textbackslash w*)*} \\
\multicolumn{3}{c}{Samples from synthesized generative models:}\\
\hline
ya&DQDF & Vr DR \\ 
glrwfdcnc&F &BeF lKQ \\
mgs&F& W\\
piljnl& KI& kqBfZ 0 \\
kj& F& ON\\
zci& GL& Bttc \\
sxpm& F& S \\
\hline
\\
\end{tabular} 
&
\begin{tabular}{c}
\begin{tabular}{l}
\multicolumn{1}{c}{Learned DSL:}\\
\hline
$f_1() = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash
u\textbackslash w*)*}\\
$f_3(x) = f_2(\scode{space}) = $\scode{( \textbar\textbackslash
u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)}\\
\emph{ (equivalent to regex `plus')}\\
$f_5() = f_4(\scode{\textbackslash l}) = \scode{\textbackslash
l*\textbackslash l}$\\
\hline
\end{tabular}
\\
\\
\includegraphics[width=.4\linewidth]{figures/nampiregexjoshcurve3.eps} 
\end{tabular}
\end{tabular}
\vspace{-.3cm}
%\caption{regex stuff}
\end{figure}

@@

    \draw [->,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
 % \caption{\system solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
\end{figure}
\begin{itemize}
\item Search finds new programs$\implies$ DSL+recognition model get more data
\item DSL improves$\implies$easier search, recognition model gets better data
  \item Recognition model improves$\implies$ easier search
  \end{itemize}

@@

>>>>

\begin{block}{Generative models of images: Turtle/LOGO Graphics}

  \newcommand{\dreamSize}{5.5cm}
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{12 (of 132) Tasks}}\\\hline
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_3_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow1_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow2_random_1.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/hexa_vh.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_5_h.png}\\
        \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/star_vh.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/spiral6_h.png}&
        \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_7_h.png}\\

%    \includegraphics[width = \dreamSize]{turtleTasks/circle/trimmed/train_circle_10_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/smooth_spiral4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/los/trimmed/train_los_3_1_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/iter2_h.png}\\\hline
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1748505267_norm.png}&
  \end{tabular}\hspace{4cm}%
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{9 samples from learned DSL}}\\\hline
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/4361002260.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/5809723215.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/5818934795_norm.png}\\
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/6027771181.png}\\
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1950268419.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/6770710484.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/7045328293.png}\\
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/7623700519.png}&
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/8879622788.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/9150025422.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/9666602433.png}\\\hline
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1748505267_norm.png}&
  \end{tabular}

  \vspace{2cm} \emph{Left:}  Agent controls a `pen' -- tasked with drawing pictures. \\\emph{Right:} During Sleep-R,
  agent `dreams' by sampling programs from learned DSL and rendering them.

@@

    \draw [->,dashed] (DSL.north) to[out = 90,in = 180] node[fill=white,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=white,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
 % \caption{\system solves for programs, the DSL, and a recognition model. Each of these steps bootstrap off of the others in a Helmholtz-machine inspired wake/sleep inference algorithm.}  \label{feeding}
\end{figure}
%% \begin{itemize}
%% \item Search finds new programs$\implies$ DSL+recognition model get more data
%% \item DSL improves$\implies$easier search, recognition model gets better data
%%   \item Recognition model improves$\implies$ easier search
%%   \end{itemize}

@@

\begin{block}{Generative models of text}
    Learn probabilistic program: a stochastic regex\begin{figure}
\centering
%\tiny
\tabcolsep=2pt
\vspace{0pt}
\begin{tabular}{cc}
\begin{tabular}{ccc}
\multicolumn{3}{c}{Tasks:}\\
\hline
cut&F &Moss Side \\ 
control&CL &Burnage \\
control&F & City Centre\\
cut& PCFL& Brooklands \\
\multicolumn{3}{c}{Learned generative models:}\\
\hline
\scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash
u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash
u\textbackslash w*)*} \\
\multicolumn{3}{c}{Samples from synthesized generative models:}\\
\hline
ya&DQDF & Vr DR \\ 
glrwfdcnc&F &BeF lKQ \\
mgs&F& W\\
piljnl& KI& kqBfZ 0 \\
kj& F& ON\\
zci& GL& Bttc \\
sxpm& F& S \\
\hline
\\
\end{tabular} 
&
\begin{tabular}{c}
\begin{tabular}{l}
\multicolumn{1}{c}{Learned DSL:}\\
\hline
$f_1() = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash
u\textbackslash w*)*}\\
$f_3(x) = f_2(\scode{space}) = $\scode{( \textbar\textbackslash
u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)}\\
\emph{ (equivalent to regex `plus')}\\
$f_5() = f_4(\scode{\textbackslash l}) = \scode{\textbackslash
l*\textbackslash l}$\\
\hline
\end{tabular}
\\
\\
\includegraphics[width=.4\linewidth]{figures/nampiregexjoshcurve3.eps} 
\end{tabular}
\end{tabular}
\vspace{-.3cm}
%\caption{regex stuff}
\end{figure}
